QPLIB: A Library of Quadratic Programming Instances

### 2017-01-27 QPLIB-1.0.tex
Add files via upload

Optimization problems with quadratic constraints and/or objective function (QP) have been the subject of a considerable amount of research over the last 60 years. At least some of the rationale for this interest is likely due to the fact that they are the ``least-nonlinear nonlinear problems''. Hence, in particular for the convex case, tools and techniques that have been honed during decades of research for Linear Programming (LP), typically with integrality constraints (MILP), can often be extended to the quadratic case with at least less effort than what would be required for tackling general Non Linear Programming (NLP) problems, without or with integrality constraints (MINLP). This has indeed happened over and over again with different algorithmic techniques, such as Interior Point methods, active-set methods (of which the simplex method is a prototypical example), enumeration methods, cut-generation techniques, reformulation techniques, and many others \todo[inline]{citations? http://www.optimization-online.org/DB\_HTML/2009/07/2338.html ?}. Similarly, nonconvex continuous QP are perhaps the ``simplest'' class of problems that require features like spatial enumeration techniques to be solved. \todo[inline]{If only the objective is quadratic, i.e., what one usually would denote by a ``nonconvex QP'', then one can ``just'' enumerate local optima. Nitpicking?} Hence, they are both the natural basis for the development of general techniques for nonconvex NLP, and a very specific class so that specialized approaches can be developed \cite{Dur2010,Burer2012}.

On the other hand, (MI)QP\todo{wasn't QP supposed to already include the mixed-integer case? so why now again MIQP?} is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many optimization problems \cite{Kochenberger2014}. Table \ref{tbl:application} provides a certainly non-exhaustive collection of applications that lead to formulations with either quadratic constraints, or quadratic objective function, or both. Also, in general any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations\todo{citations?}. Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

@@

Max-Cut & \checkmark & \cite{Rendl2008} \\ \cmidrule(rl){2-3}

@@

Packing circles$^{\ddagger}$ && \cite{hifi-mhallah:2009,szabo-etal:2005} \\ \cmidrule(rl){2-3}

@@

Pooling$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{Alfaki-Haugland:2013,Castillo-etal:2013,dambrosio-etal:2011pooling,Faria-Bagajewicz:2012,misener-floudas:2009,misener-floudas:2010-genpooling,Papageorgiou-etal:2012,pham-etal:2009,ruiz-etal:2013,visweswaran:2009}} \\ \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Unit-commitment problem} & \checkmark & \cite{Tetal15} \\

@@

@@

The structure of this paper is the following. In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP upon which the solvers we have employed are based, and \S~\ref{subsec:solver} describes the solvers. Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. Some conclusions are drawn in \S~\ref{sec:conclusions}, after which in \S~\ref{sec:instance_details} a complete description of all the instances of the library is provided\todo{and then there is \S~\ref{sec:format}}.

>>>>

Optimization problems with quadratic constraints and/or objective function (QP) have been the subject of a considerable amount of research over the last 60 years. At least some of the rationale for this interest is likely due to the fact that they are the ``least-nonlinear nonlinear problems''. Hence, in particular for the convex case, tools and techniques that have been honed during decades of research for Linear Programming (LP), typically with integrality constraints (MILP), can often be extended to the quadratic case with at least less effort than what would be required for tackling general Non Linear Programming (NLP) problems, without or with integrality constraints (MINLP). This has indeed happened over and over again with different algorithmic techniques, such as Interior Point methods, active-set methods (of which the simplex method is a prototypical example), enumeration methods, cut-generation techniques, reformulation techniques, and many others \cite{BS09}.
Similarly, nonconvex continuous QP are perhaps the ``simplest'' class of problems that require features like spatial enumeration techniques to be solved. 
Hence, they are both the natural basis for the development of general techniques for nonconvex NLP, and a very specific class so that specialized approaches can be developed \cite{Dur2010,Burer2012}.

On the other hand, (MI)QP is, in some sense, a considerably more expressive class than (MI)LP. Quadratic expressions are found, either naturally or after appropriate reformulations, in very many optimization problems \cite{Kochenberger2014}. Table \ref{tbl:application} provides a certainly non-exhaustive collection of applications that lead to formulations with either quadratic constraints, or quadratic objective function, or both. Also, in general any continuous function can be approximated with arbitrary accuracy (over a compact set) by a polynomial of arbitrary degree; in turn, every polynomial can be broken down to a system of quadratic expressions. Hence, (MI)QP is, in some sense, roughly as expressive as the whole of (MI)NLP. Of course this is, in principle, true for (MI)LP as well, but at the cost of much larger and much more complex formulations. Hence, for many applications QP may represent the ``sweet spot'' between the effectiveness, but lower expressive power, of (MI)LP and the higher expressive power, but much higher computational cost, of (MI)NLP.

@@

Max-Cut & \checkmark & \cite{Rendl2008,KrislockMalickRoupin2016} \\ \cmidrule(rl){2-3}

@@

Packing circles$^{\ddagger}$ & \checkmark & \cite{FrFG16,FGGP11,hifi-mhallah:2009,szabo-etal:2005} \\ \cmidrule(rl){2-3}

@@

Pooling$^{\ddagger}$ & \checkmark & \multirow{1}{.25\textwidth}{\cite{Alfaki-Haugland:2013,Castillo-etal:2013,dambrosio-etal:2011pooling,Faria-Bagajewicz:2012,misener-floudas:2009,misener-floudas:2010-genpooling,Papageorgiou-etal:2012,pham-etal:2009,ruiz-etal:2013}} \\ \\ \cmidrule(rl){2-3}

@@

\multirow{1}{.55\textwidth}{Unit-commitment} & \checkmark & \cite{FrFG16,FrGe06a,FrGe09a,Tetal15} \\

@@

\multicolumn{3}{l}{\textbf{Data Confidentiality}} \\[1pt]
\multirow{1}{.55\textwidth}{Controlled Tabular Adjustment} & \checkmark & \cite{CaFG14} \\

@@

The structure of this paper is the following. In \S~\ref{sec:QPbasic} we review the basic notions about QP. In particular, \S~\ref{subsec:notation} sets out the notation, \S~\ref{sec:classification} proposes a---to the best of our knowledge, new---taxonomy of QP that helps us in discussing the (very) different classes of QPs, \S~\ref{sec:algo} very briefly reviews the solution methods for QP upon which the solvers we have employed are based, and \S~\ref{subsec:solver} describes the solvers.
Then, \S~\ref{sec:lib} describes the process used to obtain the library and its results.
%; the software tools that we have used, and that are freely released together with the library, are discussed in \S~\ref{subsec:tools}. 
Some conclusions are drawn in \S~\ref{sec:conclusions}, after which Appendix A provides a complete description of all the instances of the library, while Appendix B describes the QPLIB file format.

### 2017-01-27 QPLIB-2.2.tex
Add files via upload

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%  QPLIB-2.2.tex
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

@@

Despite the apparent simplicity of the definition given in \S~\ref{subsec:notation}, Quadratic Programming instances can be of several rather different ``types'' in practice, depending on the fine details of the data. In particular, many algorithmic approaches can only be applied to QP when the data of the problem has specific properties. A taxonomy of QP instances should therefore strive to identify the set of properties that an instance should have in order to apply the most relevant computational methods. However, the sheer number of different existing approaches, and the fact that new ones are proposed, makes it hard to provide a taxonomy that is both simple and covers all possible special cases. This is why, in this paper, we propose an approach that aims at finding a good balance between simplicity and coverage of the main families of computational methods.

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Classification}\label{ssec:taxonomy}
\todo[inline]{subsubsection has some title as subsection}

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all three types\todo{or mixed integer and continuous?});
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)ua-dratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Examples and reformulations}\label{ssec:reform}
\todo{\small Ambros: maybe switch this with the next section? the next one contains more familiar material to the reader and might be an easier first introduction to the notation.}

@@

Another relevant reformulation trick concerns the fact that, as soon as quadratic constraints are allowed, then a linear objective function can be assumed w.l.o.g.. Indeed, any Q** (C*C) problem can always be rewritten as
%
\begin{align*}	
 \min \;\;
 & x^0 \\
 %
 & x^\top Q^0 x + b^0 x \leq x^0 & \\ 
 %
 & x^\top Q^i x + b^i x \leq c^i & i \in \Mcm \\ 
 %
 & l_j \leq x_j \leq u_j & j \in \Mcn  \\
 %
 & x_j \in \mathbb{Z} & j \in \Mcz
\end{align*}
%
i.e., a L*Q (L*C). Hence, it is clear that quadratic constraints are, in a well-defined sense, the most general situation (cf.~also the result above about hardness of LIQ).

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications\todo{citations?}, so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced, although this is in theory always possible.

@@

 \item \emph{Convex Continuous Quadratic Programs} CCC can be solved in polynomial time by Interior-Point techniques \cite{Wright97}; the simpler CCL can also be solved by means of ``simplex-like'' techniques, usually referred to as active-set methods \cite{Dost09}. Actually, a slightly larger class of problems can be solved with Interior-Point methods: those that can be represented by Second-Order Cone Programs. When written as QPs the corresponding $Q^i$ may not be positive semidefinite, but still the problems can be efficiently solved. Of course, these problems can still require considerable time, like LCL, when the size of the instance grows. In this sense, like in the linear case, a significant divide is from solvers that need all the data of QP to work, and those that are ``matrix-free'', i.e., only require the solution of simple operations (typically, matrix-vector products) with the data of the problem to work\todo{citations?}. While in our library we have never exploited such a characteristic, which is not suitable to the use of standard modeling tools, this may be relevant for the solution of very-large-scale CIC.

@@

 \item \emph{Nonconvex Continuous Quadratic Programs} QCQ are instead in general $\mathcal{NP}$-hard, even if the constraints are very specific (QCB) and only one eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques like the spatial Branch\&Bound\todo{citations?}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the CQC, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focussed on  \emph{exact} solution of the instances.

@@

 \item \emph{Convex Integer Quadratic Programs} CGC are in general $\mathcal{NP}$-hard, and therefore require enumerative techniques to be solved. However, convexity of the objective function and constraints implies that efficient techniques (see CCC) can be used at least to solve the continuous relaxation. The general view is that CGC are not, all other things being equal,  substantially more difficult than LGL to solve, especially if the objective function and/or the constraints have specific properties (e.g., DGL, CGL). Often integer variables are in fact binary ones, so several CCC models are C\{B,M\}C ones. In practice binary variables are considered to lead to somewhat easier problems than general integer ones (cf.~the cited result about hardness of unbounded integer quadratic programs), and several algorithmic techniques have been specifically developed for this special case. However, the general approaches for CBC are basically the same as for CGC, so there is seldom the need to distinguish between the two classes as far as solvability is concerned, although matters can be different regarding actual solution cost. Programs with only binary variables CBC can be easier than mixed-binary or integer ones C\{M,I\}C because some techniques are specifically known for the binary-only case, cf.~the next point\todo{citations?}. Absence of continuous variables, even in the presence of integer ones CIC, can also lead to specific techniques\todo{citations??}.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} QB\{B, N, L\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, among which is the reformulation of the problem as a LBL. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008}\todo{some citations? some specific problem to mention apart from Max-Cut?}.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} QGQ is the most general, and therefore is the most difficul, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, semidefinite programming relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}\todo{citations?}.

@@

This description is purposely coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flow or knapsack-type linear constraints, semi-continuous variables, or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one. It would be rather hard to collect a comprehensive list of all types of structures that may be of interest to any individual researcher, since these are as varied as the different possible approaches for specialized sub-classes of QP. For this reason we do not attempt such a more refined classification, and limit ourselves to the coarser one described in this paragraph.

>>>>

%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%  QPLIB-2.2.tex
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -
%- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

@@

Despite the apparent simplicity of the definition given in \S~\ref{subsec:notation}, Quadratic Programming instances can be of several rather different ``types'' in practice, depending on the fine details of the data. In particular, many algorithmic approaches can only be applied to QP when the data of the problem has specific properties. A taxonomy of QP instances should therefore strive to identify the set of properties that an instance should have in order to apply the most relevant computational methods. However, the sheer number of different existing approaches, and the fact that new ones are continuously proposed, makes it hard to provide a taxonomy that is both simple and covers all possible special cases. This is why, in this paper, we propose an approach that aims at finding a good balance between simplicity and coverage of the main families of computational methods.

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Taxonomy}\label{ssec:taxonomy}

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the objective function, \textit{V} the variables, and \textit{C} the constraints of the problem. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (L)inear, (D)iagonal convex quadratic, (C)onvex quadra-tic, nonconvex (Q)uadratic;
 %
 \item variables: (C)ontinuous only, (B)inary only, (M)ixed binary and continuous, (I)nteger only, (G)eneral (all other cases);
 %
 \item constraints: (N)one, (B)ox, (L)inear, (D)iagonal convex quadratic, (C)onvex quadratic, nonconvex (Q)uadratic.
\end{itemize}
%
The wildcard ``*'' will be used to indicate any possible choice, and lists of the form ``\{X, Y, Z\}'' will indicate that the value of the given field can freely attain any of the specified values.

@@

% -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -  -
\subsubsection{Examples and reformulations}\label{ssec:reform}

@@

Another relevant reformulation trick concerns the fact that, as soon as quadratic constraints are allowed, then a linear objective function can be assumed w.l.o.g.. Indeed, any Q** (C*C) problem can always be rewritten as
%
\begin{align*}	
 \min \;\;
 & x^0 \\
 %
 & -\infty \leq x^\top Q^0 x + b^0 x \leq x^0 & \\ 
 %
 & c^i_l \leq x^\top Q^i x + b^i x \leq c^i_u & i \in \Mcm \\ 
 %
 & l_j \leq x_j \leq u_j & j \in \Mcn  \\
 %
 & x_j \in \mathbb{Z} & j \in \Mcz
\end{align*}
%
i.e., a L*Q (L*C). Hence, it is clear that quadratic constraints are, in a well-defined sense, the most general situation (cf.~also the result above about hardness of LIQ).

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, since every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications (e.g., \cite{FrFG16,FrGe06a,FrGe09a,FGGP11}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced.

@@

 \item \emph{Convex Continuous Quadratic Programs} CCC can be solved in polynomial time by Interior-Point techniques \cite{Wright97}; the simpler CCL can also be solved by means of ``simplex-like'' techniques, usually referred to as active-set methods \cite{Dost09}. Actually, a slightly larger class of problems can be solved with Interior-Point methods: those that can be represented by Second-Order Cone Programs. When written as QPs the corresponding $Q^i$ may not be positive semidefinite, but still the problems can be efficiently solved. Of course, these problems can still require considerable time, like LCL, when the size of the instance grows. In this sense, like in the linear case, a significant divide is from solvers that need all the data of QP to work, and those that are ``matrix-free'', i.e., only require the solution of simple operations (typically, matrix-vector products) with the data of the problem to work. While in our library we have never exploited such a characteristic, which is not suitable to the use of standard modeling tools, this may be relevant for the solution of very-large-scale CIC.

@@

 \item \emph{Nonconvex Continuous Quadratic Programs} QCQ are instead in general $\mathcal{NP}$-hard, even if the constraints are very specific (QCB) and only one eigenvalue of $Q^0$ is negative \cite{Hemmecke2010}. They therefore require enumerative techniques like the spatial Branch\&Bound \cite{FV90,BLLMW09}, to be solved to optimality. Of course, local approaches are available that are able to efficiently provide saddle points (hopefully, local optima) of the CQC, but providing global guarantees about the quality of the obtained solutions is challenging. In our library we have specifically focussed on  \emph{exact} solution of the instances.

@@

 \item \emph{Convex Integer Quadratic Programs} CGC are in general $\mathcal{NP}$-hard, and therefore require enumerative techniques to be solved. However, convexity of the objective function and constraints implies that efficient techniques (see CCC) can be used at least to solve the continuous relaxation. The general view is that CGC are not, all other things being equal,  substantially more difficult than LGL to solve, especially if the objective function and/or the constraints have specific properties (e.g., DGL, CGL). Often integer variables are in fact binary ones, so several CCC models are C\{B,M\}C ones. In practice binary variables are considered to lead to somewhat easier problems than general integer ones (cf.~the cited result about hardness of unbounded integer quadratic programs), and several algorithmic techniques have been specifically developed for this special case. However, the general approaches for CBC are basically the same as for CGC, so there is seldom the need to distinguish between the two classes as far as solvability is concerned, although matters can be different regarding actual solution cost. Programs with only binary variables CBC can be easier than mixed-binary or integer ones C\{M,I\}C because some techniques are specifically known for the binary-only case, cf.~the next point \cite{BEP09}. Absence of continuous variables, even in the presence of integer ones CIC, can also lead to specific techniques \cite{BEL13}.

@@

  \item \emph{Nonconvex Binary Quadratic Programs} QB\{B, N, L\} obviously are $\mathcal{NP}$-hard. However, the special nature of binary variables combined with quadratic forms allows for quite specific techniques to be developed, among which is the reformulation of the problem as a LBL. Also, many well-known combinatorial problems can be naturally reformulated as problems of this class, and therefore a considerable number of results have been obtained by exploiting specific properties of the set of constraints \cite{Rendl2008,Loiola2007657}.

@@

  \item \emph{Nonconvex Integer Quadratic Programs} QGQ is the most general, and therefore is the most difficul, class. Due to the lack of convexity even when integrality requirements are removed, solution methods must typically combine several algorithmic ideas, such as enumeration (distinguishing the role of integral variables from that of continuous ones involved into nonconvex terms) and techniques (e.g., outer approximation, semidefinite programming relaxation, \ldots) that allow to efficiently compute bounds. As in the convex case, QBQ, QMQ, and QIQ can benefit from more specific properties of the variables \cite{Buchheim2013,Dong2016}.

@@

This description is purposely coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flow \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11}, or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}. It would be rather hard to collect a comprehensive list of all types of structures that may be of interest to any individual researcher, since these are as varied as the different possible approaches for specialized sub-classes of QP. For this reason we do not attempt such a more refined classification, and limit ourselves to the coarser one described in this paragraph.
